Tesseroids: forward modeling gravitational fields in spherical coordinates

### 2015-03-01 manuscript.tex
Move Reproducing to the end of Implementation

\pdfoutput=1
%\documentclass[paper,twocolumn]{geophysics}
%\documentclass[manuscript]{geophysics}
%\documentclass[manuscript,endfloat]{geophysics}
\documentclass[twocolumn]{article}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\newcommand{\mitbf}[1]{\mathbf{{#1}}}

@@

\textit{Tesseroids}  consists of command-line programs
written in the C programming language.
The command-line interface follows the Unix principals of
(1) making each program do one thing well,
(2) using plain text for input and output,
(3) making each program a ``filter'' that can be used in conjunction with other
programs.
The package includes programs to calculate
the gravitational fields of tesseroids and
rectangular prisms (in both Cartesian and spherical coordinates),
as well as model and computation grid generation.
All programs receive input through
command-line arguments and the standard input channel (STDIN)
and output the results through the standard output channel (STDOUT).
For example,
the command to generate a regular grid with $NLON \times NLAT$ points,
calculate on it $g_z$ and $g_{zz}$ caused by
the tesseroids in a file ``MODELFILE'',
and save the results to a file called ``OUTPUT''
is:

@@

All figures and numerical experiments in this article
were produced by IPython notebooks\footnote{
\href{http://ipython.org}{http://ipython.org}}
\citep{Perez2007}.
These files combine the analysis and figure generation source code
with text, equations, and the figures generated by the code.
We used \textit{pandas} by \citet{Mckinney2010}
to perform the data analysis,
\textit{matplotlib} by \citet{Hunter2007} for graphs,
and \textit{Mayavi} by \citet{Ramachandran2011} for 3D graphs.

The notebook files,
as well as instructions for installing and running the analysis,
are distributed along with the source code archive
that accompanies this article.
Alternatively,
all accompanying material can be downloaded
from an online source code repository\footnote{
\href{https://github.com/pinga-lab/paper-tesseroids}{https://github.com/pinga-lab/paper-tesseroids}}
or a persistent archive\footnote{
\href{}{\todo[inline]{Replace with the Zenodo DOI for the repo.}}}.

@@

@@

We perform the analysis on the largest error.

>>>>

\pdfoutput=1
%\documentclass[paper,twocolumn]{geophysics}
%\documentclass[manuscript]{geophysics}
%\documentclass[manuscript,endfloat]{geophysics}
\documentclass{article}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}
\newcommand{\mitbf}[1]{\mathbf{{#1}}}

@@

\textit{Tesseroids}  consists of command-line programs
written in the C programming language.
The package includes programs to calculate
the gravitational fields of tesseroids and
rectangular prisms (in both Cartesian and spherical coordinates),
as well as model and computation grid generation.
All programs receive input through
command-line arguments and the standard input channel (STDIN)
and output the results through the standard output channel (STDOUT).
For example,
the command to generate a regular grid with $NLON \times NLAT$ points,
calculate on it $g_z$ and $g_{zz}$ caused by
the tesseroids in a file ``MODELFILE'',
and save the results to a file called ``OUTPUT''
is:

@@

@@

All figures and numerical experiments in this article
were produced in IPython notebooks\footnote{
\href{http://ipython.org}{http://ipython.org}}
\citep{Perez2007}.
These files combine the analysis and figure generation source code
with text, equations, and the figures generated by the code.
We used \textit{pandas} by \citet{Mckinney2010}
to perform the data analysis,
\textit{matplotlib} by \citet{Hunter2007} for graphs,
and \textit{Mayavi} by \citet{Ramachandran2011} for 3D graphs.

The notebook files,
as well as instructions for installing and running the analysis,
are distributed along with the source code archive
that accompanies this article.
Alternatively,
all accompanying material can be downloaded
from an online source code repository\footnote{
\href{https://github.com/pinga-lab/paper-tesseroids}{https://github.com/pinga-lab/paper-tesseroids}}
or a persistent archive\footnote{
\href{}{\todo[inline]{Replace with the Zenodo/figshare DOI for the repo.}}}.

@@

We compute the differences between the effects of the shell and the tesseroid
model on the grid and keep only the largest error.
